---
title: "Car Data"
author: "Kshitij Patl"
date: "November 5, 2020"
output: pdf
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r}
rm(list=ls())
library(plotly)
library(data.table)
library(tidyr)
library(lubridate)
library(zoo)
```
## Understanding Gas Mileage

Using the `mtcars` dataset we plot can attempt to understand the relationship
of various factors to gas mileage (`mpg`).

We plot weight (`wt`) vs. mileage (`mpg`) spatially along the x/y axes. We 
visualize the number of cylinders (`cyl`) as colors and the amount of
horsepower (`hp`) as the size of an individual point in the plot.

accidents <- fread("data/Accidents0514.csv", header = TRUE, 
                       sep = ",")
accidents <- accidents %>%
  select(Accident_Severity, Date)

accidents1 <- fread("data/Accidents_2015.csv", header = TRUE, 
                     sep = ",")
accidents1 <- accidents1 %>%
  select(Accident_Severity, Date)

# concatenate data tables and free up environment
accidents <- rbind(accidents, accidents1)
rm(list = c("accidents", "accidents1"))

## Visualizing the Data

```{r plot, echo=FALSE}
plot_ly(data = mtcars, x = ~wt, y = ~mpg, 
        color = ~as.factor(cyl), size = ~hp,
        text = ~paste("Weight: ", wt, '<br>MPG:', mpg),
        type = "bar", mode = "markers") %>%
  layout(title = "Mileage Data")
```

